---
title: "`r paste0(yourname, ' - CV')`"
author: "`Zachary Gold`"
date: "`r format(Sys.Date(), format='%B %d, %Y')`"
params:
  pdf_mode:
    value: true
  cache_data:
    value: true
output:
  pagedown::html_resume:
    css: ['styles_cv.css', 'resume']
    self_contained: true


---

```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}

/* @import url("https://fonts.googleapis.com/css?family=Montserrat|Playfair+Display&display=swap");
-1 */
@import url("https://fonts.googleapis.com/css?family=Lato:300,400,900");
@import url('https://fonts.googleapis.com/css?family=Muli:400,400i,700&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Roboto+Slab:wght@100;400;900&display=swap');
@import url('https://fonts.googleapis.com/css2?family=Roboto&family=Roboto+Slab:wght@100;400;900&display=swap');

/* Main text is monserrat*/

body {
  font-family: 'Roboto', sans-serif;
  font-weight: 300;
  line-height: 1.1;
  color:  #0055A4;
}

/* Give headers playfair font */

h2 {
  font-family: 'Roboto Slab', serif;
  font-weight: 00;
  color:  #0055A4;
}

h3 {
  font-family: 'Roboto Slab', serif;
  font-weight: 00;
  color: black;
}
 
h1 {
  font-family: 'Roboto Slab', serif;
  font-weight: 900;
  color: #0055A4;
}

title {
    font-family: 'Roboto Slab', serif;
    font-weight: 900;
    color: #0055A4;
    /* font-size: 15px; */
}

.title {
    font-family: 'Roboto Slab', serif;
    font-weight: 900;
    color:#00467F;
    /* font-size: 15px; */
}

/* Change the color of all links (hyperlinks) */
a {
  color: #0093D0; /* Green links */
}


/* When in PDF export mode make sure superscripts are nice and small and italic */
sup {
  font-size: 0.45rem;
  font-style: italic;
}

/* Avoid the breaking within a section */
.blocks {
  break-inside: avoid;
}

* {
  /* Override default right margin for sidebar*/
  --pagedjs-margin-right: 0.2in;
  --pagedjs-margin-left: 0.2in;
}

/* Customize some of the sizing variables */
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 12rem;
  --sidebar-background-color: #ffffff;
  --sidebar-horizontal-padding: 0.01in; /* Reduce sidebar padding */
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
  --decorator-border: 2px solid #ffffff; /* Make timeline a blue as well*/
}



.details .place {
  margin-top: 0.25rem;
}

.main-block:not(.concise) .details div {
  padding-top: 0.005rem;
}

/* Laptop icon isn't centered by default which is lame */
.fa-laptop {
  margin-left: -3px;
}

/* When we have links at bottom in a list make sure they actually are numbered */
#links li {
  list-style-type: decimal;
}

/* Dont put the little fake list point in front of links */
.aside li::before {
  display: none;
}

/* Move closer to start and up towards header */
.aside ul {
  padding-left: 1rem;
}

.aside li::before {
  position: relative;
  margin-left: -5pt;
  content: "• ";
}

/* Make sure elements in asside are centered and have a nice small text */
.aside {
  width: calc(var(--sidebar-width) + 9px);
  line-height: 1.2;
  font-size: 0.75rem;
}

/* Make little circle outline be a light blue */
.decorator::after {
  background-color: #FFFFFF;
}

/* Remove the fake bullets from lists */
.aside li::before {
  content: auto;
}

.skill-bar {
  color: white;
  padding: 0.1rem 0.25rem;
  margin-top: 3px;
  position: relative;
  width: 100%;
}

/* When the class no-timeline is added we remove the after psuedo element from the header... */

/* Removes the psuedo element on h2 tags for this section */
.section.no-timeline h2::after {
  content: none;
}

/* Without adding padding the content is all up on the title */
.section.no-timeline h2 {
  padding-bottom: 1rem;
}

/* Add styles for little cards  */
.info-card {
  width: 220px;
  float: left;
  padding: 0.5rem;
  margin: 0.5rem;
  box-shadow: 1px 1px 4px black;
}

/* Make the network viz go up near the top */
svg {
  margin-top: -1.25in;
}


<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>



```



```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

CV <- readr::read_rds('cached_positions.rds')
CV$entries_data <- 
  CV$entries_data %>%
    dplyr::filter(public_cv == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r format(Sys.Date(), format='%B %d, %Y')`.


Main
================================================================================

**`Zachary Gold`** {#title}
--------------------------------------------------------------------------------


```{r}
# Note the special double pipe so we modify the CV object in place
#CV %<>% print_text_block("intro") 
```



Appointments {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('positions')
```

Professional Service {data-icon=fish}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('prof_service')

```



Professional Affiliations  {data-icon=fish}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section(section_id = 'proff_affil')

```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Awards and Honors  {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```


Grants {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('grants')
```

Peer Reviewed Publications  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

Technical and Government Reports  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('technical_memo')
```


Presentations  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('presentations')
```

Outreach {data-icon=ship}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('outreach')
```

Conferences and Workshops {data-icon=ship}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('conferences')
```

Mentorship {data-icon=user-plus}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('mentor')
```



Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching')
```


Journal Reviews {data-icon=user-plus}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('journal_reviews')
```

Proposal Reviews {data-icon=user-plus}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('proposal_reviews')
```

Skills {data-icon=user-plus}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('skills')
```











